\bf The forestecology R package for fitting and assessing models of interspecies competitive effects on the growth of trees

### 2021-03-04 paper/forestecology.Rmd
resolved all TODO's and started following submission guidelines

- name: David Allen
  affiliation: Biology Department, Middlebury College

@@

bibliography: paper.bib
output: rticles::asa_article
link-citations: yes
header-includes:
- \usepackage{xcolor, soul, xspace, float, subfig, lineno}
---

\linenumbers

@@

@@

The output `growth_scbi` is a single data frame of class `sf` that includes variables `growth`, the average annual growth in DBH (cm y^-1^) for all stems that were alive at both time points, and `geometry`, the `sf` package's encoding of geolocations of type `<POINT>`. Furthermore, the variables that should remain unchanged between censuses appear only once, such as location variables `gx` and `gy`; as well as species-related variables. Variables that should change between censuses are suffixed with `1` and `2` indicating the earlier and later censuses, such as `dbh1/dbh2` and `codes1/codes2`. Site data that does not align with this convention will need to be transformed for use with the `compute_growth()` function. However, in the end, all that matters is that the growth of all stems is saved in a data frame of class `sf` and, at a minimum, the data contains the variables above. Lastly, the species variable `sp` is automatically converted to a factor^[In our spatial cross-validation algorithm in Section \ref{spatial-cross-validation} issues can occur when rare species do not occur in the training set, but then are encountered in the test set. This risk is mitigated by representing `sp` as a factor variable, which has a complete list of all levels of the categorical variable.].

TODO: enumerate what these variables are and say if they need exact names

Given that `growth_scbi` is of class `sf`, it can be easily plotted in `ggplot2` using the `geom_sf()` geometry as seen in Figure \ref{fig:scbi-trees}.

```{r scbi-trees, out.width="66%", fig.cap="Compute growth of trees based on census data: Map with growth of all trees from a 9 ha subsection of the Smithsonian Conservation Biology Institute (SCBI) forest plot."}
# TODO: Rescale points in this plot
ggplot() +
  geom_sf(data = growth_scbi, aes(size = growth)) + 
  scale_size(breaks = c(0.01, 0.1, 1), range = c(0.1, 1))
```

@@

The next step in our analysis sequence is to identify all focal trees and their corresponding competitor trees. The `create_focal_vs_comp()` functions performs these tasks and returns a new data frame of type `sf`. On top of the previous arguments `comp_dist` defining the competition neighborhood and `id` indicating which variable uniquely identifies each tree-stem, this function also requires an `sf` object representation of the spatial cross-validation blocks/folds. In this example, the blocks were manually encoded in `blocks_scbi` by specifying it's vertices in Section \ref{spatial-information}^[We present an alternative method for defining spatial cross-validation blocks is using the `spatialBlock()` function from the `blockCV` package in the Appendix]. We present the resulting data frame below with the `foldID` variable omitted for compactness of presentation.

```{r scbi-focal-vs-comp}
# TODO: Below reconcile the number of rows as they off by one from growth_scbi %>% 
# filter(!is.na(growth) & !buffer). Perhaps by removing NA's in the growth_scbi stage?
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID")
focal_vs_comp_scbi %>% 
  select(-foldID)
```

@@

```{r, eval = FALSE}
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp")
```
```{r scbi-focal-vs-comp-3, echo = FALSE}
# Not sure why we need to do things this way:
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp") %>% 
  print(n = 5)
```

@@

```{r scbi-model-fit}
# TODO: Add information about default priors in ?comp_bayes_lm()
comp_bayes_lm_scbi <- focal_vs_comp_scbi %>%
  comp_bayes_lm(prior_param = NULL)
```

@@

@@

The authors thank Ryan Giordano and Jonathan Che for their help with the statistical methodology and Sophie Li for their feedback on package interface.

>>>>

- name: David N. Allen
  affiliation: Biology Department, Middlebury College

@@

spacing: double

bibliography: paper.bib
output: rticles::asa_article
link-citations: yes
header-includes:
- \usepackage{xcolor, soul, xspace, float, subfig, lineno, setspace}
- \linenumbers
---

@@

\doublespacing

@@

The output `growth_scbi` is a single data frame of class `sf` that includes variables `growth`, the average annual growth in DBH (cm y^-1^) for all stems that were alive at both time points, and `geometry`, the `sf` package's encoding of geolocations of type `<POINT>`. In addition the species variable `sp` is converted to a factor if it wasn't already by `compute_growth()`.^[In our spatial cross-validation algorithm in Section \ref{spatial-cross-validation} issues can occur when rare species do not occur in the training set, but then are encountered in the test set. This risk is mitigated by representing `sp` as a factor variable, which has a complete list of all levels of the categorical variable.] Furthermore, the variables that should remain unchanged between censuses appear only once, such as location variables `gx` and `gy`; as well as species-related variables. Variables that should change between censuses are suffixed with `1` and `2` indicating the earlier and later censuses, such as `dbh1/dbh2` and `codes1/codes2`.

Site data that does not align with this convention will need to be transformed for use with the `compute_growth()` function. However, in the end, all that matters is that the growth of all stems is saved in a data frame of class `sf` and, at a minimum, contains the variable uniquely identifying each stem, `sp`, `dbh1`, `growth`, `geometry`.

Given that `growth_scbi` is of class `sf`, it can be easily plotted in `ggplot2` using the `geom_sf()` geometry as seen in Figure \ref{fig:scbi-trees} where we plot a random sample of 500 out of the `r nrow(growth_scbi)` trees.

```{r scbi-trees, out.width="66%", fig.cap="Compute growth of trees based on census data: Map with growth of a random sample of 500 trees from a 9 ha subsection of the Smithsonian Conservation Biology Institute (SCBI) forest plot."}
ggplot() +
  geom_sf(data = growth_scbi %>% sample_n(500), aes(size = growth)) + 
  scale_size_binned(limits = c(0.1, 1))
```

@@

The next step in our analysis sequence is to identify all focal trees and their corresponding competitor trees. More specifically, it identifies all trees that are not part of the buffer region, have a valid `growth` measurement, and have at least one neighbor within `r comp_dist` of it.  The `create_focal_vs_comp()` functions performs these tasks and returns a new data frame of type `sf`. On top of the previous arguments `comp_dist` defining the competition neighborhood and `id` indicating which variable uniquely identifies each tree-stem, this function also requires an `sf` object representation of the spatial cross-validation blocks/folds. In this example, the blocks were manually encoded in `blocks_scbi` by specifying it's vertices in Section \ref{spatial-information}^[We present an alternative method for defining spatial cross-validation blocks is using the `spatialBlock()` function from the `blockCV` package in the Appendix]. We present the resulting data frame below with the `foldID` variable omitted for compactness of presentation.

```{r scbi-focal-vs-comp}
focal_vs_comp_scbi <- growth_scbi %>%
  create_focal_vs_comp(comp_dist, blocks = blocks_scbi, id = "stemID")
focal_vs_comp_scbi %>% 
  select(-foldID)
```

```{r, eval = FALSE, echo = FALSE}
# Internal: after removing trees in buffer and have NA for growth, there is one
# tree that is not included in focal_vs_comp_scbi b/c it has no neighbors within
# comp_dist = 7.5m of it
growth_scbi %>% 
  filter(!buffer & !is.na(growth)) %>% 
  filter(!stemID %in% focal_vs_comp_scbi$focal_ID)

growth_scbi %>% 
  mutate(flag = stemID == 18823) %>% 
  ggplot() +
  geom_sf(aes(col = flag))
```

@@

```{r, scbi-focal-vs-comp-3}
focal_vs_comp_scbi %>% 
  filter(focal_ID == 4) %>% 
  select(focal_ID, dbh, comp) %>% 
  unnest(cols = "comp")
```

@@

```{r scbi-model-fit}
comp_bayes_lm_scbi <- focal_vs_comp_scbi %>%
  comp_bayes_lm(prior_param = NULL)
```

@@

The `forestecology` package provides

@@

The authors thank Ryan Giordano and Jonathan Che for their help with the statistical methodology and Sophie Li for their feedback on package interface. The authors declare no conflicts of interest.

# Author's contributions

A.Y.K. and D.N.A. conceived the ideas and coded most of the package in the early design stages. A.Y.K. led the writing of the manuscript. S.P.C. refactored much of the package's code in the later design stages to align with R and "tidy" programming best practices [@wickham_welcome_2019]. All authors contributed critically to the drafts and gave final approval for publication.

# Data accessibility

We intend to archive all data and code on GitHub at the following repository https://github.com/rudeboybert/forestecology. This repository will be versioned and archived on Zenodo upon acceptance.

### 2021-03-04 paper/forestecology.tex
resolved all TODO's and started following submission guidelines

\usepackage{xcolor, soul, xspace, float, subfig, lineno}

@@

  \author{
        Albert Y. Kim \\
    Program in Statistical \& Data Sciences, Smith College\\
     and \\     David Allen \\
    Biology Department, Middlebury College\\
     and \\     Simon P. Couch \\
    Mathematics Department, Reed College\\
      }
  \maketitle
} \fi

@@

\linenumbers

@@

The output \texttt{growth\_scbi} is a single data frame of class
\texttt{sf} that includes variables \texttt{growth}, the average annual
growth in DBH (cm y\textsuperscript{-1}) for all stems that were alive
at both time points, and \texttt{geometry}, the \texttt{sf} package's
encoding of geolocations of type
\texttt{\textless{}POINT\textgreater{}}. Furthermore, the variables that
should remain unchanged between censuses appear only once, such as
location variables \texttt{gx} and \texttt{gy}; as well as
species-related variables. Variables that should change between censuses
are suffixed with \texttt{1} and \texttt{2} indicating the earlier and
later censuses, such as \texttt{dbh1/dbh2} and \texttt{codes1/codes2}.
Site data that does not align with this convention will need to be
transformed for use with the \texttt{compute\_growth()} function.
However, in the end, all that matters is that the growth of all stems is
saved in a data frame of class \texttt{sf} and, at a minimum, the data
contains the variables above. Lastly, the species variable \texttt{sp}
is automatically converted to a factor\footnote{In our spatial
  cross-validation algorithm in Section \ref{spatial-cross-validation}
  issues can occur when rare species do not occur in the training set,
  but then are encountered in the test set. This risk is mitigated by
  representing \texttt{sp} as a factor variable, which has a complete
  list of all levels of the categorical variable.}.

TODO: enumerate what these variables are and say if they need exact
names

Given that \texttt{growth\_scbi} is of class \texttt{sf}, it can be
easily plotted in \texttt{ggplot2} using the \texttt{geom\_sf()}
geometry as seen in Figure \ref{fig:scbi-trees}.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# }\AlertTok{TODO}\CommentTok{: Rescale points in this plot}
\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi, }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{size =}\NormalTok{ growth)) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{scale_size}\NormalTok{(}\DataTypeTok{breaks =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.01}\NormalTok{, }\FloatTok{0.1}\NormalTok{, }\DecValTok{1}\NormalTok{), }\DataTypeTok{range =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.1}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\caption{Compute growth of trees based on census data: Map with growth of all trees from a 9 ha subsection of the Smithsonian Conservation Biology Institute (SCBI) forest plot.}\label{fig:scbi-trees}
\end{figure}

@@

The next step in our analysis sequence is to identify all focal trees
and their corresponding competitor trees. The
\texttt{create\_focal\_vs\_comp()} functions performs these tasks and
returns a new data frame of type \texttt{sf}. On top of the previous
arguments \texttt{comp\_dist} defining the competition neighborhood and
\texttt{id} indicating which variable uniquely identifies each
tree-stem, this function also requires an \texttt{sf} object
representation of the spatial cross-validation blocks/folds. In this
example, the blocks were manually encoded in \texttt{blocks\_scbi} by
specifying it's vertices in Section \ref{spatial-information}\footnote{We
  present an alternative method for defining spatial cross-validation
  blocks is using the \texttt{spatialBlock()} function from the
  \texttt{blockCV} package in the Appendix}. We present the resulting
data frame below with the \texttt{foldID} variable omitted for
compactness of presentation.

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# }\AlertTok{TODO}\CommentTok{: Below reconcile the number of rows as they off by one from growth_scbi %>% }
\CommentTok{# filter(!is.na(growth) & !buffer). Perhaps by removing NA's in the growth_scbi stage?}
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{foldID)}
\CommentTok{## # A tibble: 6,296 x 6}
\CommentTok{##   focal_ID focal_sp   dbh   geometry growth comp             }
\CommentTok{##      <dbl> <fct>    <dbl>    <POINT>  <dbl> <list>           }
\CommentTok{## 1        4 nysy     13.6  (14.2 428)  0.103 <tibble [20 x 4]>}
\CommentTok{## 2        5 havi      8.8   (9.4 436)  0.150 <tibble [32 x 4]>}
\CommentTok{## 3       79 tiam     47.7    (40 381) -0.161 <tibble [20 x 4]>}
\CommentTok{## 4       80 caca      5.15 (38.7 422)  0.253 <tibble [12 x 4]>}
\CommentTok{## 5       96 libe      2.3    (60 310)  0.262 <tibble [14 x 4]>}
\CommentTok{## # ... with 6,291 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(focal_ID }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(focal_ID, dbh, comp) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{unnest}\NormalTok{(}\DataTypeTok{cols =} \StringTok{"comp"}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

\begin{verbatim}
## # A tibble: 20 x 6
##   focal_ID   dbh comp_ID  dist comp_sp comp_basal_area
##      <dbl> <dbl>   <dbl> <dbl> <fct>             <dbl>
## 1        4  13.6    1836  7.48 tiam            0.0176 
## 2        4  13.6    1847  2.81 nysy            0.00332
## 3        4  13.6    1848  1.62 nysy            0.00396
## 4        4  13.6    1849  2.62 nysy            0.00535
## 5        4  13.6    1850  2.98 havi            0.00472
## # ... with 15 more rows
\end{verbatim}

@@

\begin{Shaded}
\begin{Highlighting}[]
\CommentTok{# }\AlertTok{TODO}\CommentTok{: Add information about default priors in ?comp_bayes_lm()}
\NormalTok{comp_bayes_lm_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{comp_bayes_lm}\NormalTok{(}\DataTypeTok{prior_param =} \OtherTok{NULL}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{cv_grid =}\NormalTok{ blocks_scbi)}
\end{Highlighting}
\end{Shaded}

@@

@@

The authors thank Ryan Giordano and Jonathan Che for their help with the
statistical methodology and Sophie Li for their feedback on package
interface.

>>>>

\usepackage{xcolor, soul, xspace, float, subfig, lineno, setspace}
\linenumbers

@@

  \author{
        Albert Y. Kim \\
    Program in Statistical \& Data Sciences, Smith College\\
     and \\     David N. Allen \\
    Biology Department, Middlebury College\\
     and \\     Simon P. Couch \\
    Mathematics Department, Reed College\\
      }
  \maketitle
} \fi

@@

\doublespacing

@@

The output \texttt{growth\_scbi} is a single data frame of class
\texttt{sf} that includes variables \texttt{growth}, the average annual
growth in DBH (cm y\textsuperscript{-1}) for all stems that were alive
at both time points, and \texttt{geometry}, the \texttt{sf} package's
encoding of geolocations of type
\texttt{\textless{}POINT\textgreater{}}. In addition the species
variable \texttt{sp} is converted to a factor if it wasn't already by
\texttt{compute\_growth()}.\footnote{In our spatial cross-validation
  algorithm in Section \ref{spatial-cross-validation} issues can occur
  when rare species do not occur in the training set, but then are
  encountered in the test set. This risk is mitigated by representing
  \texttt{sp} as a factor variable, which has a complete list of all
  levels of the categorical variable.} Furthermore, the variables that
should remain unchanged between censuses appear only once, such as
location variables \texttt{gx} and \texttt{gy}; as well as
species-related variables. Variables that should change between censuses
are suffixed with \texttt{1} and \texttt{2} indicating the earlier and
later censuses, such as \texttt{dbh1/dbh2} and \texttt{codes1/codes2}.

Site data that does not align with this convention will need to be
transformed for use with the \texttt{compute\_growth()} function.
However, in the end, all that matters is that the growth of all stems is
saved in a data frame of class \texttt{sf} and, at a minimum, contains
the variable uniquely identifying each stem, \texttt{sp}, \texttt{dbh1},
\texttt{growth}, \texttt{geometry}.

Given that \texttt{growth\_scbi} is of class \texttt{sf}, it can be
easily plotted in \texttt{ggplot2} using the \texttt{geom\_sf()}
geometry as seen in Figure \ref{fig:scbi-trees} where we plot a random
sample of 500 out of the 7954 trees.

\begin{Shaded}
\begin{Highlighting}[]
\KeywordTok{ggplot}\NormalTok{() }\OperatorTok{+}
\StringTok{  }\KeywordTok{geom_sf}\NormalTok{(}\DataTypeTok{data =}\NormalTok{ growth_scbi }\OperatorTok{%>%}\StringTok{ }\KeywordTok{sample_n}\NormalTok{(}\DecValTok{500}\NormalTok{), }\KeywordTok{aes}\NormalTok{(}\DataTypeTok{size =}\NormalTok{ growth)) }\OperatorTok{+}\StringTok{ }
\StringTok{  }\KeywordTok{scale_size_binned}\NormalTok{(}\DataTypeTok{limits =} \KeywordTok{c}\NormalTok{(}\FloatTok{0.1}\NormalTok{, }\DecValTok{1}\NormalTok{))}
\end{Highlighting}
\end{Shaded}

@@

\caption{Compute growth of trees based on census data: Map with growth of a random sample of 500 trees from a 9 ha subsection of the Smithsonian Conservation Biology Institute (SCBI) forest plot.}\label{fig:scbi-trees}
\end{figure}

@@

The next step in our analysis sequence is to identify all focal trees
and their corresponding competitor trees. More specifically, it
identifies all trees that are not part of the buffer region, have a
valid \texttt{growth} measurement, and have at least one neighbor within
7.5 of it. The \texttt{create\_focal\_vs\_comp()} functions performs
these tasks and returns a new data frame of type \texttt{sf}. On top of
the previous arguments \texttt{comp\_dist} defining the competition
neighborhood and \texttt{id} indicating which variable uniquely
identifies each tree-stem, this function also requires an \texttt{sf}
object representation of the spatial cross-validation blocks/folds. In
this example, the blocks were manually encoded in \texttt{blocks\_scbi}
by specifying it's vertices in Section
\ref{spatial-information}\footnote{We present an alternative method for
  defining spatial cross-validation blocks is using the
  \texttt{spatialBlock()} function from the \texttt{blockCV} package in
  the Appendix}. We present the resulting data frame below with the
\texttt{foldID} variable omitted for compactness of presentation.

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{growth_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{create_focal_vs_comp}\NormalTok{(comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi, }\DataTypeTok{id =} \StringTok{"stemID"}\NormalTok{)}
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(}\OperatorTok{-}\NormalTok{foldID)}
\CommentTok{## # A tibble: 6,296 x 6}
\CommentTok{##   focal_ID focal_sp   dbh   geometry growth comp             }
\CommentTok{##      <dbl> <fct>    <dbl>    <POINT>  <dbl> <list>           }
\CommentTok{## 1        4 nysy     13.6  (14.2 428)  0.103 <tibble [20 x 4]>}
\CommentTok{## 2        5 havi      8.8   (9.4 436)  0.150 <tibble [32 x 4]>}
\CommentTok{## 3       79 tiam     47.7    (40 381) -0.161 <tibble [20 x 4]>}
\CommentTok{## 4       80 caca      5.15 (38.7 422)  0.253 <tibble [12 x 4]>}
\CommentTok{## 5       96 libe      2.3    (60 310)  0.262 <tibble [14 x 4]>}
\CommentTok{## # ... with 6,291 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{filter}\NormalTok{(focal_ID }\OperatorTok{==}\StringTok{ }\DecValTok{4}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(focal_ID, dbh, comp) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{unnest}\NormalTok{(}\DataTypeTok{cols =} \StringTok{"comp"}\NormalTok{)}
\CommentTok{## # A tibble: 20 x 6}
\CommentTok{##   focal_ID   dbh comp_ID  dist comp_sp comp_basal_area}
\CommentTok{##      <dbl> <dbl>   <dbl> <dbl> <fct>             <dbl>}
\CommentTok{## 1        4  13.6    1836  7.48 tiam            0.0176 }
\CommentTok{## 2        4  13.6    1847  2.81 nysy            0.00332}
\CommentTok{## 3        4  13.6    1848  1.62 nysy            0.00396}
\CommentTok{## 4        4  13.6    1849  2.62 nysy            0.00535}
\CommentTok{## 5        4  13.6    1850  2.98 havi            0.00472}
\CommentTok{## # ... with 15 more rows}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{comp_bayes_lm_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{comp_bayes_lm}\NormalTok{(}\DataTypeTok{prior_param =} \OtherTok{NULL}\NormalTok{)}
\end{Highlighting}
\end{Shaded}

@@

\begin{Shaded}
\begin{Highlighting}[]
\NormalTok{focal_vs_comp_scbi <-}\StringTok{ }\NormalTok{focal_vs_comp_scbi }\OperatorTok{%>%}
\StringTok{  }\KeywordTok{run_cv}\NormalTok{(}\DataTypeTok{comp_dist =}\NormalTok{ comp_dist, }\DataTypeTok{blocks =}\NormalTok{ blocks_scbi)}
\end{Highlighting}
\end{Shaded}

@@

The \texttt{forestecology} package provides

@@

The authors thank Ryan Giordano and Jonathan Che for their help with the
statistical methodology and Sophie Li for their feedback on package
interface. The authors declare no conflicts of interest.

\hypertarget{authors-contributions}{%
\section{Author's contributions}\label{authors-contributions}}

A.Y.K. and D.N.A. conceived the ideas and coded most of the package in
the early design stages. A.Y.K. led the writing of the manuscript.
S.P.C. refactored much of the package's code in the later design stages
to align with R and ``tidy'' programming best practices
\citep{wickham_welcome_2019}. All authors contributed critically to the
drafts and gave final approval for publication.

\hypertarget{data-accessibility}{%
\section{Data accessibility}\label{data-accessibility}}

We intend to archive all data and code on GitHub at the following
repository \url{https://github.com/rudeboybert/forestecology}. This
repository will be versioned and archived on Zenodo upon acceptance.
